---
title: "CMIP & Obs Comparison Ocean pH"
aauthor: "K. Dorheim"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
    toc: TRUE
    toc_float:
      collapsed: true
      toc_depth : 2

   
---
<!---
```{r opts, echo = FALSE}
knitr::opts_chunk$set(
  fig.path = "images/"
)
```
--->



```{r environment set up, echo = FALSE, warning = FALSE}
# Libs
library(knitr)
library(ggplot2)

# Define the paths to figs directorries
BASE_NAME <- "C:/Users/dorh012/Documents/GitHub/OA_variability/figs"
INDVID_MODELS_PATH  <- paste0(BASE_NAME, "/cmip/individual_models")
MULTIP_MODELS_PATH  <- paste0(BASE_NAME, "/cmip")
OBS_COMPARISON_PATH <- paste0(BASE_NAME, "/observations")


# Define the markdown function 

# The print_list function will take an unnested list and print all of the figures saved there
print_list <- function(list){
  
  for(i in 1:length(list)){
    
    if(!is.null(list[[i]])){
          print(list[[i]])
    }
  }
  
} # end of the print_list function

```



 
 
# Observation vs CMIP 
**** 
For all of these figures the cmip basins have been redefined to match the area of the observational data. The observation data sets are sometimes misleading labeled as a model, my bad it is just on the bottom of my to do list.

## BATS comparison 
*** 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
path <- list.files(OBS_COMPARISON_PATH, "BATS.rd", full.names = TRUE)
obs_list <- get(load(path))
``` 

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$monthly_mean
``` 


## HOTS comparison 
*** 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
path <- list.files(OBS_COMPARISON_PATH, "HOTS.rd", full.names = TRUE)
obs_list <- get(load(path))
``` 


#### ph

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$monthly_mean
``` 


#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
obs_list$spco2$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$monthly_mean
``` 


#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$monthly_mean
``` 

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$monthly_mean
``` 

## ESTOC comparison 
*** 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
path <- list.files(OBS_COMPARISON_PATH, "ESTOC", full.names = TRUE)
obs_list <- get(load(path))
``` 


#### ph

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$monthly_mean
``` 


#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$monthly_mean
``` 


#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$monthly_mean
``` 

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
obs_list$co3$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$monthly_mean
```  

## Flinders Reef comparison 
*** 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
path <- list.files(OBS_COMPARISON_PATH, "Flinders", full.names = TRUE)
obs_list <- get(load(path))
``` 


#### ph

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$monthly_mean
``` 


#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$monthly_mean
``` 


#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$monthly_mean
``` 

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$monthly_mean
``` 

## Iceland Sea comparison 
*** 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
path <- list.files(OBS_COMPARISON_PATH, "Iceland", full.names = TRUE)
obs_list <- get(load(path))
``` 


#### ph

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$monthly_mean
``` 


#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$monthly_mean
``` 


#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$monthly_mean
``` 

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$monthly_mean
```  

## Irminger Sea comparison 
*** 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
path <- list.files(OBS_COMPARISON_PATH, "Irminger", full.names = TRUE)
obs_list <- get(load(path))
``` 


#### ph

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$monthly_mean
``` 


#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$monthly_mean
``` 


#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$monthly_mean
``` 

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$monthly_mean
``` 
