---
title: "Ocean pH"
author: "K. Dorheim"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
    toc: TRUE
    toc_float:
      collapsed: true
      toc_depth : 2

   
---

```{r opts, echo = FALSE}
knitr::opts_chunk$set(
  fig.path = "images/"
)
```




```{r environment set up, echo = FALSE, warning = FALSE}
# Libs
library(knitr)
library(ggplot2)

# Define the paths to figs directorries
BASE_NAME <- "C:/Users/dorh012/Documents/GitHub/OA_variability/figs"
INDVID_MODELS_PATH  <- paste0(BASE_NAME, "/cmip/individual_models")
MULTIP_MODELS_PATH  <- paste0(BASE_NAME, "/cmip")
OBS_COMPARISON_PATH <- paste0(BASE_NAME, "/observations")


# Define the markdown function 

# The print_list function will take an unnested list and print all of the figures saved there
print_list <- function(list){
  
  for(i in 1:length(list)){
    
    if(!is.null(list[[i]])){
          print(list[[i]])
    }
  }
  
} # end of the print_list function

```

# Methodology 
****

None of the variables in question have depth information. 

#### L1: Process CMIP5 Netcdfs
1. CDO - Concatenate cmip netcdfs and convert to absolute time 
2. CDO - Get the field weighted mean via cdo 
3. R - Remove model with unrealistic or missing pH/CO3 observations 
4. R - Concatenate the all of the csv files created on pic into a single RData object

<br>

#### L2: Detrend
1. R - detrend the basin means using a 3rd degre polynomial (see GitHub issue # 11 for decision)

#### L3: Analyze Detrended Data
Monthly Mean - monthly mean over a 30 year period. 
Amplitude - annual range

<br>

# Processed Observations 
***

```{r, echo = FALSE, warning = FALSE}
table_path <- list.files(paste0(BASE_NAME,"/cmip"), "observations_table", full.names = TRUE)
tables <- get(load(table_path))
```

### Model observations removed from analysis
```{r, echo = FALSE, warning = FALSE}
tables$observations_removed
```

<br>

### Model observations processed
```{r, echo = FALSE, warning = FALSE}
tables$experiment_variable
```


<br>


# Individual Models
****

## 1. CESM1-BGC
****

```{r, echo = FALSE, warning = FALSE}

fig_path <- list.files(INDVID_MODELS_PATH, "CESM1", full.names = TRUE)
figures_list <- get(load(fig_path))

```

### Time Series Comparison
****


This section currently only displays the historical & future rcp time series for the Global ocean basins but can be modified to incldue other basins. The histoircal & rcp cmip observations were detrended separtely using a third degree polynomail. The figures below contain historical & future rcp observations on the same plot for visual purposes to make comparing the data before and after detrending easier.

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$ph
figures_list$detrended_tseries$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$spco2
figures_list$detrended_tseries$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$tos
figures_list$detrended_tseries$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$co3
figures_list$detrended_tseries$co3
```


<br>

### Monthly Mean 


Monthly Means over 30 year periods.

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$co3
```

<br>

### Seasonal Amplitude Time Series

The time series of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$co3
```

<br>

### Seasonal Amplitude Distirbution

Distirbution of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$co3
```


### K and S Figures
 
#### K historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter$K)
```


#### S historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter$S)
```

#### Delta K and S

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$deltaKS_scatter[[1]]
```

<br>

#### Annual Extremes

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$ph$max
figures_list$extreme_heat_map$ph$min
```
 
```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$spco2$max
figures_list$extreme_heat_map$spco2$min
``` 
 
```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$tos$max
figures_list$extreme_heat_map$tos$min
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$co3$max
figures_list$extreme_heat_map$co3$min
``` 
 
## 2. IPSL
****

```{r, echo = FALSE, warning = FALSE}
fig_path <- list.files(INDVID_MODELS_PATH, "IPSL", full.names = TRUE)
figures_list <- get(load(fig_path))
```

### Time Series Comparison
****

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$ph
figures_list$detrended_tseries$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$spco2
figures_list$detrended_tseries$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$tos
figures_list$detrended_tseries$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$co3
figures_list$detrended_tseries$co3
```


<br>

### Monthly Mean 


Monthly Means over 30 year periods.

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$co3
```

<br>

### Seasonal Amplitude Time Series

The time series of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$co3
```

<br>

### Seasonal Amplitude Distirbution

Distirbution of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$co3
```


### K and S Figures
 
#### K historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter$K)
```


#### S historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter$S)
```

#### Delta K and S

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$deltaKS_scatter[[1]]
```
 
 
#### Annual Extremes

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$ph$max
figures_list$extreme_heat_map$ph$min
```
 
```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$spco2$max
figures_list$extreme_heat_map$spco2$min
``` 
 
```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$tos$max
figures_list$extreme_heat_map$tos$min
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$co3$max
figures_list$extreme_heat_map$co3$min
``` 
## 3. CMCC-CESM
****

```{r, echo = FALSE, warning = FALSE}
fig_path <- list.files(INDVID_MODELS_PATH, "CMCC-CESM", full.names = TRUE)
figures_list <- get(load(fig_path))
```

### Time Series Comparison
****

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$ph
figures_list$detrended_tseries$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$spco2
figures_list$detrended_tseries$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$tos
figures_list$detrended_tseries$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$co3
figures_list$detrended_tseries$co3
```


<br>

### Monthly Mean 


Monthly Means over 30 year periods.

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$co3
```

<br>

### Seasonal Amplitude Time Series

The time series of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$co3
```

<br>

### Seasonal Amplitude Distirbution

Distirbution of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$co3
```


### K and S Figures
 
#### K historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter$K)
```


#### S historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter$S)
```

#### Delta K and S

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$deltaKS_scatter[[1]]
``` 


#### Annual Extremes

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$ph$max
figures_list$extreme_heat_map$ph$min
```
 
```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$spco2$max
figures_list$extreme_heat_map$spco2$min
``` 
 
```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$tos$max
figures_list$extreme_heat_map$tos$min
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$co3$max
figures_list$extreme_heat_map$co3$min
``` 

## 4. MPI-ESM-LR
****

```{r, echo = FALSE, warning = FALSE}
fig_path <- list.files(INDVID_MODELS_PATH, "MPI-ESM-LR", full.names = TRUE)
figures_list <- get(load(fig_path))
```

### Time Series Comparison
****

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$ph
figures_list$detrended_tseries$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$spco2
figures_list$detrended_tseries$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$tos
figures_list$detrended_tseries$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$co3
figures_list$detrended_tseries$co3
```


<br>

### Monthly Mean 


Monthly Means over 30 year periods.

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$co3
```

<br>

### Seasonal Amplitude Time Series

The time series of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$co3
```

<br>

### Seasonal Amplitude Distirbution

Distirbution of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$co3
```


### K and S Figures
 
#### K historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter$K)
```


#### S historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter$S)
```

#### Delta K and S

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$deltaKS_scatter[[1]]
```
 
 
#### Annual Extremes

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$ph$max
figures_list$extreme_heat_map$ph$min
```
 
```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$spco2$max
figures_list$extreme_heat_map$spco2$min
``` 
 
```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$tos$max
figures_list$extreme_heat_map$tos$min
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$co3$max
figures_list$extreme_heat_map$co3$min
``` 

## 5. MPI-ESM-MR
****

```{r, echo = FALSE, warning = FALSE}
fig_path <- list.files(INDVID_MODELS_PATH, "MPI-ESM-MR", full.names = TRUE)
figures_list <- get(load(fig_path))
```

### Time Series Comparison
****

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$ph
figures_list$detrended_tseries$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$spco2
figures_list$detrended_tseries$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$tos
figures_list$detrended_tseries$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$co3
figures_list$detrended_tseries$co3
```


<br>

### Monthly Mean 


Monthly Means over 30 year periods.

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$co3
```

<br>

### Seasonal Amplitude Time Series

The time series of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$co3
```

<br>

### Seasonal Amplitude Distirbution

Distirbution of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$co3
```


### K and S Figures
 
#### K historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter$K)
```


#### S historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter$S)
```

#### Delta K and S

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$deltaKS_scatter[[1]]
```
 
 
#### Annual Extremes

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$ph$max
figures_list$extreme_heat_map$ph$min
```
 
```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$spco2$max
figures_list$extreme_heat_map$spco2$min
``` 
 
```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$tos$max
figures_list$extreme_heat_map$tos$min
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$co3$max
figures_list$extreme_heat_map$co3$min
``` 

## 6. HadGEM2-CC
****

```{r, echo = FALSE, warning = FALSE}
fig_path <- list.files(INDVID_MODELS_PATH, "HadGEM2-CC", full.names = TRUE)
figures_list <- get(load(fig_path))
```

### Time Series Comparison
****

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$ph
figures_list$detrended_tseries$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$spco2
figures_list$detrended_tseries$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$tos
figures_list$detrended_tseries$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$co3
figures_list$detrended_tseries$co3
```


<br>

### Monthly Mean 


Monthly Means over 30 year periods.

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$co3
```

<br>

### Seasonal Amplitude Time Series

The time series of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$co3
```

<br>

### Seasonal Amplitude Distirbution

Distirbution of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$co3
```


### K and S Figures
 
#### K historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter$K)
```


#### S historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter$S)
```

#### Delta K and S

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$deltaKS_scatter[[1]]
```
 
 
#### Annual Extremes

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$ph$max
figures_list$extreme_heat_map$ph$min
```
 
```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$spco2$max
figures_list$extreme_heat_map$spco2$min
``` 
 
```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$tos$max
figures_list$extreme_heat_map$tos$min
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$co3$max
figures_list$extreme_heat_map$co3$min
``` 

## 7. GFDL-ESM2G
****

```{r, echo = FALSE, warning = FALSE}
fig_path <- list.files(INDVID_MODELS_PATH, "GFDL-ESM2G", full.names = TRUE)
figures_list <- get(load(fig_path))
```

### Time Series Comparison
****

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$ph
figures_list$detrended_tseries$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$spco2
figures_list$detrended_tseries$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$tos
figures_list$detrended_tseries$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$co3
figures_list$detrended_tseries$co3
```


<br>

### Monthly Mean 


Monthly Means over 30 year periods.

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$co3
```

<br>

### Seasonal Amplitude Time Series

The time series of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$co3
```

<br>

### Seasonal Amplitude Distirbution

Distirbution of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$co3
```


### K and S Figures
 
#### K historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter$K)
```


#### S historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter$S)
```

#### Delta K and S

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$deltaKS_scatter[[1]]
```
 
 
#### Annual Extremes

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$ph$max
figures_list$extreme_heat_map$ph$min
```
 
```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$spco2$max
figures_list$extreme_heat_map$spco2$min
``` 
 
```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$tos$max
figures_list$extreme_heat_map$tos$min
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$co3$max
figures_list$extreme_heat_map$co3$min
```  

## 8. GFDL-ESM2M
****

```{r, echo = FALSE, warning = FALSE}
fig_path <- list.files(INDVID_MODELS_PATH, "GFDL-ESM2M", full.names = TRUE)
figures_list <- get(load(fig_path))
```

### Time Series Comparison
****

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$ph
figures_list$detrended_tseries$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$spco2
figures_list$detrended_tseries$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$tos
figures_list$detrended_tseries$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$co3
figures_list$detrended_tseries$co3
```


<br>

### Monthly Mean 


Monthly Means over 30 year periods.

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$co3
```

<br>

### Seasonal Amplitude Time Series

The time series of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$co3
```

<br>

### Seasonal Amplitude Distirbution

Distirbution of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$co3
```


### K and S Figures
 
#### K historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter$K)
```


#### S historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter$S)
```

#### Delta K and S

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$deltaKS_scatter[[1]]
```
 
 
#### Annual Extremes

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$ph$max
figures_list$extreme_heat_map$ph$min
```
 
```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$spco2$max
figures_list$extreme_heat_map$spco2$min
``` 
 
```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$tos$max
figures_list$extreme_heat_map$tos$min
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$co3$max
figures_list$extreme_heat_map$co3$min
```  

## 9. HadGEM2-ES
****

```{r, echo = FALSE, warning = FALSE}
fig_path <- list.files(INDVID_MODELS_PATH, "HadGEM2-ES", full.names = TRUE)
figures_list <- get(load(fig_path))
```

### Time Series Comparison
****

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$ph
figures_list$detrended_tseries$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$spco2
figures_list$detrended_tseries$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$tos
figures_list$detrended_tseries$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$raw_tseries$co3
figures_list$detrended_tseries$co3
```


<br>

### Monthly Mean 


Monthly Means over 30 year periods.

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$monthly_mean$co3
```

<br>

### Seasonal Amplitude Time Series

The time series of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_tseries$co3
```

<br>

### Seasonal Amplitude Distirbution

Distirbution of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$amplitude_density$co3
```


### K and S Figures
 
#### K historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter$K)
```


#### S historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter$S)
```

#### Delta K and S

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$deltaKS_scatter[[1]]
```

 
 
#### Annual Extremes

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$ph$max
figures_list$extreme_heat_map$ph$min
```
 
```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$spco2$max
figures_list$extreme_heat_map$spco2$min
``` 
 
```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$tos$max
figures_list$extreme_heat_map$tos$min
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$extreme_heat_map$co3$max
figures_list$extreme_heat_map$co3$min
``` 

# Multiple Models
```{r, echo = FALSE, warning = FALSE}
data_path <- list.files(MULTIP_MODELS_PATH, "multiple_models_figures", full.names = TRUE)
figures_list <- get(load(data_path))
```

### Time Series Comparison
****

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$time_series$raw$ph
figures_list$time_series$detrended$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$time_series$raw$spco2
figures_list$time_series$detrended$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$time_series$raw$tos
figures_list$time_series$detrended$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$time_series$raw$co3
figures_list$time_series$detrended$co3
```


<br>

### Monthly Mean 


Monthly Means over 30 year periods.

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$mean_monthly$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$mean_monthly$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$mean_monthly$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$mean_monthly$co3
```

<br>

### Seasonal Amplitude Time Series

The time series of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$time_series$amplitude$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$time_series$amplitude$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$time_series$amplitude$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$time_series$amplitude$co3
```

<br>

### Seasonal Amplitude Distirbution

Distirbution of annual seasonal amplitude for each variable / basin. 

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$distribution$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$distribution$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$distribution$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$distribution$co3
```


### K and S Figures
 
#### K historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter_figs$K)
```


#### S historical vs future 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(figures_list$KS_scatter_figs$S)
```

# Delta K and S

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$delta_K
```



## 11. Delta K & S Tables 


```{r laod the K and S tables, echo = FALSE, warning = FALSE}
table_path <- list.files(paste0(BASE_NAME,"/cmip"), "delta_KS_tables", full.names = TRUE)
TABLES <- get(load(table_path))
```

#### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
TABLES$ph
```

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
TABLES$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
TABLES$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
TABLES$co3
```




 
 
# Amplitude Sameness

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
fig_path <- list.files(MULTIP_MODELS_PATH, "amplitude_sameness", full.names = TRUE)
sameness_list <- get(load(fig_path))
```


## Amplitude Sameness Figures

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print_list(sameness_list$figures)
```


## Percent Within "Sameness Index"

The precent of observations that are within the similarity band.

#### ph 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
sameness_list$within$ph
```


#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
sameness_list$within$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
sameness_list$within$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
sameness_list$within$co3
```


## Percent Above "Sameness Index"

The precent of observations that are above the similarity band.

#### ph 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
sameness_list$above$ph
```


#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
sameness_list$above$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
sameness_list$above$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
sameness_list$above$co3
```

## Percent Below "Sameness Index"

The precent of observations that are below the similarity band.

#### ph 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
sameness_list$below$ph
```


#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
sameness_list$below$spco2
```

#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
sameness_list$below$tos
```

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
sameness_list$below$co3
```








 
  

# Annual Extreme Sameness

### pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$annual_extremes$ph$max
```


```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$annual_extremes$ph$min
```

The models agree more on the timing of the annual min value than they do on the timing of the max. 

### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$annual_extremes$spco2$max
```


```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$annual_extremes$spco2$min
```

Where as in spco2 the models agree more on the timing of the annual max. 


### tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$annual_extremes$tos$max
```


```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$annual_extremes$tos$min
```

Timing of the max and min values are consitent over time and across models for tos.

### co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$annual_extremes$co3$max
```


```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
figures_list$annual_extremes$co3$min
```

CO3 in the southern ocean we see the signal of a temporal change in the timing of the min. Min is occurring earlier in the winter season, may be cause summer is occuring earlier? 


# Observation vs CMIP 
**** 
For all of these figures the cmip basins have been redefined to match the area of the observational data. The observation data sets are sometimes misleading labeled as a model, my bad it is just on the bottom of my to do list.

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
compar_path <- list.files(OBS_COMPARISON_PATH, ".rd", full.names = TRUE)
sameness_list <- get(load(fig_path))
``` 


## BATS comparison 
*** 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
path <- list.files(OBS_COMPARISON_PATH, "BATS.rd", full.names = TRUE)
obs_list <- get(load(path))
``` 

#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$monthly_mean
``` 


## HOTS comparison 
*** 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
path <- list.files(OBS_COMPARISON_PATH, "HOTS.rd", full.names = TRUE)
obs_list <- get(load(path))
``` 


#### ph

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$monthly_mean
``` 


#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
obs_list$spco2$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$monthly_mean
``` 


#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$monthly_mean
``` 

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$monthly_mean
``` 

## ESTOC comparison 
*** 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
path <- list.files(OBS_COMPARISON_PATH, "ESTOC", full.names = TRUE)
obs_list <- get(load(path))
``` 


#### ph

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$monthly_mean
``` 


#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$monthly_mean
``` 


#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$monthly_mean
``` 

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
obs_list$co3$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$monthly_mean
```  

## Flinders Reef comparison 
*** 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
path <- list.files(OBS_COMPARISON_PATH, "Flinders", full.names = TRUE)
obs_list <- get(load(path))
``` 


#### ph

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$monthly_mean
``` 


#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$monthly_mean
``` 


#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$monthly_mean
``` 

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$monthly_mean
``` 

## Iceland Sea comparison 
*** 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
path <- list.files(OBS_COMPARISON_PATH, "Iceland", full.names = TRUE)
obs_list <- get(load(path))
``` 


#### ph

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$monthly_mean
``` 


#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$monthly_mean
``` 


#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$monthly_mean
``` 

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$monthly_mean
```  

## Irminger Sea comparison 
*** 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
path <- list.files(OBS_COMPARISON_PATH, "Irminger", full.names = TRUE)
obs_list <- get(load(path))
``` 


#### ph

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$ph$monthly_mean
``` 


#### spco2

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$spco2$monthly_mean
``` 


#### tos

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$tos$monthly_mean
``` 

#### co3

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$raw_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$detrended_tsereis
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_tseries
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$amp_distribution
``` 

```{r, echo = FALSE, warning = FALSE, fig.height=10, fig.width=10}
obs_list$co3$monthly_mean
``` 
