---
title: "Ocean pH"
author: "K. Dorheim"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
    toc: TRUE
    toc_float:
      collapsed: true
      toc_depth : 4

   
---

# House Keeping Notes
****

# Methodology 
****

None of the variables in question have depth information. 

#### L1
1. CDO - Concatenate cmip netcdfs and convert to absolute time 
2. CDO - Get the field weighted mean via cdo 
3. R - Remove model with unrealistic or missing pH/CO3 observations 
4. R - Concatenate the all of the csv files created on pic into a single RData object

<br>

#### L2
1. R - detrend the basin means using a 3rd degre polynomial (see GitHub issue # 11 for decision)

<br>


```{r laod detrending cesm1 figures, echo = FALSE, warning = FALSE}
path <- "C:/Users/dorh012/Documents/GitHub/OA_variability/data/figs"
detrending_figs <- get(load(paste0(path, "/detrend_cesm1.rda")))
```

# CESM1-BGC Detrended data
****

## By Variable

<br>

### 1. a. Historical pH

```{r, echo = FALSE, warning = FALSE, fig.width = 9, fig.height = 7}
detrending_figs$historical$ph
```

<br>

### 1. b. RCP 8.5 pH


```{r, echo = FALSE, warning = FALSE, fig.width = 9, fig.height = 7}
detrending_figs$rcp85$ph
```

<br>

### 1. c. Historical spCO2

```{r, echo = FALSE, warning = FALSE, fig.width = 9, fig.height = 7}
detrending_figs$historical$spco2
```

<br>

### 1. d. RCP 8.5 spCO2

```{r, echo = FALSE, warning = FALSE, fig.width = 9, fig.height = 7}
detrending_figs$rcp85$spco2
```

<br>

### 1. e. Historical tos

```{r, echo = FALSE, warning = FALSE, fig.width = 9, fig.height = 7}
detrending_figs$historical$tos
```

<br>

### 1. f. RCP 8.5 tos

```{r, echo = FALSE, warning = FALSE, fig.width = 9, fig.height = 7}
detrending_figs$rcp85$tos
```


The End
