---
title: "Ocean pH"
author: "K. Dorheim"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
    toc: TRUE
    toc_float:
      collapsed: true
      toc_depth : 4

   
---

```{r opts, echo = FALSE}
knitr::opts_chunk$set(
  fig.path = "images/"
)
```

# New Stuff

New figures include the seasonal amplitude time series and seasonal amplitude distribution for CESM1-BGC. Last time we spoke there was some interest expressed in the IPSL model so I have included the same plots for CESM1-BGC but for IPSL. However IPSL did not do spco2 runs so there are no figures for that. 

I also included time series and amplitude figures of all of the models, however these figures are fairly cluttered and hard to interpret.


# Methodology 
****

None of the variables in question have depth information. 

#### L1: Process CMIP5 Netcdfs
1. CDO - Concatenate cmip netcdfs and convert to absolute time 
2. CDO - Get the field weighted mean via cdo 
3. R - Remove model with unrealistic or missing pH/CO3 observations 
4. R - Concatenate the all of the csv files created on pic into a single RData object

<br>

#### L2: Detrend
1. R - detrend the basin means using a 3rd degre polynomial (see GitHub issue # 11 for decision)

#### L3: Analyze Detrended Data
Monthly Mean - monthly mean over a 30 year period. 
Amplitude - annual range


<br>


```{r laod cesm1 figures, echo = FALSE, warning = FALSE}
library(ggplot2)
path <- "C:/Users/dorh012/Documents/GitHub/OA_variability/data/figs"
CESM1 <- get(load(paste0(path, "/FIGS.CESM1.rda")))
```




# CESM1-BGC
****

## 1. Time Series Comparison
****


This section currently only displays the historical & future rcp time series for the Global ocean basins but can be modified to incldue other basins. The histoircal & rcp cmip observations were detrended separtely using a third degree polynomail. The figures below contain historical & future rcp observations on the same plot for visual purposes to make comparing the data before and after detrending easier.


### 1.a. pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
CESM1$time_series$raw$ph + labs(subtitle = "Before Detrending", caption = "") + theme(text = element_text(size = 18))
CESM1$time_series$detrended$ph + labs(subtitle = "After Detrending", caption = "") + theme(text = element_text(size = 18))
```

### 1.b. spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
CESM1$time_series$raw$spco2 + labs(subtitle = "Before Detrending", caption = "") + theme(text = element_text(size = 18))
CESM1$time_series$detrended$spco2 + labs(subtitle = "After Detrending", caption = "") + theme(text = element_text(size = 18))
```

### 1.c. tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
CESM1$time_series$raw$tos + labs(subtitle = "Before Detrending", caption = "") + theme(text = element_text(size = 18))
CESM1$time_series$detrended$tos + labs(subtitle = "After Detrending", caption = "") + theme(text = element_text(size = 18))
```

### 1.d. co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
CESM1$time_series$raw$co3 + labs(subtitle = "Before Detrending", caption = "") + theme(text = element_text(size = 18))
CESM1$time_series$detrended$co3 + labs(subtitle = "After Detrending", caption = "") + theme(text = element_text(size = 18))
```


## 2. Monthly Mean 
****

Monthly Means over 30 year periods.

### 2.a. pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
CESM1$mean_monthly$ph + theme(text = element_text(size = 18))
```

### 2.b. spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
CESM1$mean_monthly$spco2 + theme(text = element_text(size = 18))
```

### 2.c. tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
CESM1$mean_monthly$tos + theme(text = element_text(size = 18))
```

### 2.d. co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
CESM1$mean_monthly$co3 + theme(text = element_text(size = 18))
```


## 3. Seasonal Amplitude Time Series
****

The time series of annual seasonal amplitude for each variable / basin. 

### 3.a. pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
CESM1$time_series$amplitude$ph + theme(text = element_text(size = 18))
```

### 3.b. spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
CESM1$time_series$amplitude$spco2 + theme(text = element_text(size = 18))
```

### 3.c. tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
CESM1$time_series$amplitude$tos + theme(text = element_text(size = 18))
```

### 3.d. co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
CESM1$time_series$amplitude$co3 + theme(text = element_text(size = 18))
```



## 4. Seasonal Amplitude Distirbution
****

Distirbution of annual seasonal amplitude for each variable / basin. 

### 4.a. pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
CESM1$distribution$ph + theme(text = element_text(size = 18))
```

### 4.b. spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
CESM1$distribution$spco2 + theme(text = element_text(size = 18))
```

### 4.c. tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
CESM1$distribution$tos + theme(text = element_text(size = 18))
```

### 4.d. co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
CESM1$distribution$co3 + theme(text = element_text(size = 18))
```

 
```{r laod IPSL figures, echo = FALSE, warning = FALSE}
remove(CESM1)
path <- "C:/Users/dorh012/Documents/GitHub/OA_variability/data/figs"
IPSL <- get(load(paste0(path, "/FIGS.IPSL.rda")))
```


# IPSL
****

## 5. Time Series Comparison
****

This section currently only displays the historical & future rcp time series for the Global ocean basins but can be modified to incldue other basins. The histoircal & rcp cmip observations were detrended separtely using a third degree polynomail. The figures below contain historical & future rcp observations on the same plot for visual purposes to make comparing the data before and after detrending easier.


### 5.a. pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
IPSL$time_series$raw$ph + labs(subtitle = "Before Detrending", caption = "") + theme(text = element_text(size = 18))
IPSL$time_series$detrended$ph + labs(subtitle = "After Detrending", caption = "") + theme(text = element_text(size = 18))
```

### 5.b. spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print("No spco2 for IPSL")
```

### 5.c. tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
IPSL$time_series$raw$tos + labs(subtitle = "Before Detrending", caption = "") + theme(text = element_text(size = 18))
IPSL$time_series$detrended$tos + labs(subtitle = "After Detrending", caption = "") + theme(text = element_text(size = 18))
```

### 5.d. co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
IPSL$time_series$raw$co3 + labs(subtitle = "Before Detrending", caption = "") + theme(text = element_text(size = 18))
IPSL$time_series$detrended$co3 + labs(subtitle = "After Detrending", caption = "") + theme(text = element_text(size = 18))
```

<br>


## 6. Monthly Mean 
****

Monthly Means over 30 year periods.

### 6.a. pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
IPSL$mean_monthly$ph + theme(text = element_text(size = 18))
```

### 6.b. spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print("No spco2 for IPSL")
```

### 6.c. tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
IPSL$mean_monthly$tos + theme(text = element_text(size = 18))
```

### 6.d. co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
IPSL$mean_monthly$co3 + theme(text = element_text(size = 18))
```


## 7. Seasonal Amplitude Time Series
****

The time series of annual seasonal amplitude for each variable / basin. 

### 7.a. pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
IPSL$time_series$amplitude$ph + theme(text = element_text(size = 18))
```

### 7.b. spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print("No spco2 for IPSL")
```

### 7.c. tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
IPSL$time_series$amplitude$tos + theme(text = element_text(size = 18))
```

### 7.d. co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
IPSL$time_series$amplitude$co3 + theme(text = element_text(size = 18))
```


## 8. Seasonal Amplitude Distirbution
****

Distirbution of annual seasonal amplitude for each variable / basin. 

### 8.a. pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
IPSL$distribution$ph + theme(text = element_text(size = 18))
```

### 8.b. spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
print("No spco2 for IPSL")
```

### 8.c. tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
IPSL$distribution$tos + theme(text = element_text(size = 18))
```

### 8.d. co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
IPSL$distribution$co3 + theme(text = element_text(size = 18))
```


 
```{r laod all figures, echo = FALSE, warning = FALSE}
remove(IPSL)
path <- "C:/Users/dorh012/Documents/GitHub/OA_variability/data/figs"
ALL <- get(load(paste0(path, "/FIGS.ALL.rda")))
```


# All Models
****

## 9. Time Series Comparison
****

This section currently only displays the historical & future rcp time series for the Global ocean basins but can be modified to incldue other basins. The histoircal & rcp cmip observations were detrended separtely using a third degree polynomail. The figures below contain historical & future rcp observations on the same plot for visual purposes to make comparing the data before and after detrending easier.


### 9.a. pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
ALL$time_series$raw$ph + labs(subtitle = "Before Detrending", caption = "") + theme(text = element_text(size = 18))
ALL$time_series$detrended$ph + labs(subtitle = "After Detrending", caption = "") + theme(text = element_text(size = 18))
```

### 9.b. spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
ALL$time_series$raw$spco2 + labs(subtitle = "Before Detrending", caption = "") + theme(text = element_text(size = 18))
ALL$time_series$detrended$spco2 + labs(subtitle = "After Detrending", caption = "") + theme(text = element_text(size = 18))
```

### 9.c. tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
ALL$time_series$raw$tos + labs(subtitle = "Before Detrending", caption = "") + theme(text = element_text(size = 18))
ALL$time_series$detrended$tos + labs(subtitle = "After Detrending", caption = "") + theme(text = element_text(size = 18))
```

### 9.d. co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
ALL$time_series$raw$co3 + labs(subtitle = "Before Detrending", caption = "") + theme(text = element_text(size = 18))
ALL$time_series$detrended$co3 + labs(subtitle = "After Detrending", caption = "") + theme(text = element_text(size = 18))
```

### 2.c. co3

```{r, echo = FALSE, warning = FALSE, fig.height=12, fig.width=12}
ALL$mean_monthly$co3 + theme(text = element_text(size = 17))
```


## 3. Monthly Range 
****


## 10. Seasonal Amplitude Time Series
****

The time series of annual seasonal amplitude for each variable / basin. 

### 10.a. pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
ALL$time_series$amplitude$ph + theme(text = element_text(size = 18))
```

### 10.b. spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
ALL$time_series$amplitude$spco2 + theme(text = element_text(size = 18))
```

### 10.c. tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
ALL$time_series$amplitude$tos + theme(text = element_text(size = 18))
```

### 10.d. co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
ALL$time_series$amplitude$tos + theme(text = element_text(size = 18))
```

### 3.b. spco2

```{r, echo = FALSE, warning = FALSE, fig.height=12, fig.width=12}
ALL$monthly_range$spco2 + theme(text = element_text(size = 17))
```


## 11. Seasonal Amplitude Distirbution
****

Distirbution of annual seasonal amplitude for each variable / basin. 

### 11.a. pH

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
ALL$distribution$ph + theme(text = element_text(size = 18))
```

### 11.b. spco2

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
ALL$distribution$spco2 + theme(text = element_text(size = 18))
```

### 11.c. tos

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
ALL$distribution$tos + theme(text = element_text(size = 18))
```

### 11.d. co3

```{r, echo = FALSE, warning = FALSE, fig.height=14, fig.width=14}
ALL$distribution$co3 + theme(text = element_text(size = 18))
```



The End


 
 
